---
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(dplyr)
devtools::load_all()
```
## Testing performance of the `individual` package
This repo uses the SIR model with changing population described in the tutorial [here](https://mrc-ide.github.io/individual/articles/Tutorial.html) as an example for benchmarking performance of `individual` against pure C++ code.

We compare performance of the R model against 1. a model written entirely in C++ using the C++ components of `individual` and 2. an `individual` R model that uses custom "prefab" C++ processes.

### Closed SIR Model
```{r closed-benchmark, echo=FALSE}
N <- 1e3
I0 <- 5
S0 <- N - I0
dt <- 0.1
tmax <- 100

gamma <- 1 / 10
R0 <- 2.5
health_states <- c("S", "I", "R")

bm <- bench::mark(
  run_R_model(N, I0, dt, tmax, gamma, R0),
  run_C_model(N, I0, dt, tmax, gamma, R0),
  run_R_model_with_prefabs(N, I0, dt, tmax, gamma, R0),
  check = FALSE
)

data.frame(model_version = c("R", "C", "Prefab"),
           median_time_seconds = as.numeric(bm$median),
           speedup = signif(as.numeric(bm$median[[1]]) / as.numeric(bm$median), 2))
```

### Open SIR Model
```{r open-benchmark, echo=FALSE}

birth_rate <- 2
death_rate <- .001

bm <- bench::mark(
  run_R_model(N, I0, dt, tmax, gamma, R0, birth_rate, death_rate),
  run_C_model(N, I0, dt, tmax, gamma, R0, birth_rate, death_rate),
  run_R_model_with_prefabs(N, I0, dt, tmax, gamma, R0, birth_rate, death_rate),
  check = FALSE
)

data.frame(model_version = c("R", "C", "Prefab"),
           median_time_seconds = as.numeric(bm$median),
           speedup = signif(as.numeric(bm$median[[1]]) / as.numeric(bm$median), 2))
```

## Profiling c++ code
1. install system deps:
   ```{bash eval=FALSE}
    sudo apt install \
    libgoogle-perftools-dev \
    libprotoc-dev libprotobuf-dev protobuf-compiler \
    golang-go \
    graphviz
   ```

2. install `pprof`:
   `go install github.com/google/pprof@latest`
3. install this package:
   `R CMD INSTALL .`
4. run the profiling script:
   `./profile/run_profiler.sh`
